My title\thanks{Code and data are available at: \url{https://github.com/RohanAlexander/starter_folder}.}

### 2024-11-14 paper/paper.tex

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome
variable or update the subheading to be singular.

Some of our data is of penguins (Figure~\ref{fig-bills}), from Horst,
Hill, and Gorman (2020).

\includegraphics{paper_files/figure-pdf/fig-bills-1.pdf}

\caption{\label{fig-bills}Bills of penguins}

Talk more about it.

And also planes (Figure~\ref{fig-planes}). (You can change the height
and width, but don't worry about doing that until you have finished
every other aspect of the paper - Quarto will try to make it look nice
and the defaults usually work well once you have enough text.)

\includegraphics{paper_files/figure-pdf/fig-planes-1.pdf}

\caption{\label{fig-planes}Relationship between wing length and width}

Talk way more about it.

@@

\begin{Shaded}
\begin{Highlighting}[]
\DocumentationTok{\#\#\#\# Read data \#\#\#\#}
\CommentTok{\# Load the cleaned dataset}
\NormalTok{analysis\_data }\OtherTok{\textless{}{-}} \FunctionTok{read\_csv}\NormalTok{(}\StringTok{"C:/Users/eliza/Downloads/hammer{-}3{-}compressed/cleaned\_price\_changes.csv"}\NormalTok{, }\AttributeTok{show\_col\_types =} \ConstantTok{FALSE}\NormalTok{)}

\CommentTok{\# Generate plot for Average Current Price by Vendor}
\NormalTok{vendor\_price\_plot }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(vendor\_name) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{avg\_price\_current =} \FunctionTok{mean}\NormalTok{(price\_current, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(vendor\_name, avg\_price\_current), }\AttributeTok{y =}\NormalTok{ avg\_price\_current)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{stat =} \StringTok{"identity"}\NormalTok{, }\AttributeTok{fill =} \StringTok{"skyblue"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Average Current Price by Vendor"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Vendor"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Average Current Price (CAD)"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}

\CommentTok{\# Display the plot}
\NormalTok{vendor\_price\_plot}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-4-1.pdf}

Figure 1: Average Current Price by Vendor. This bar plot shows the
average price of products sold by each grocery vendor in Canadian
dollars (CAD). Variations in pricing suggest differences in market
positioning or pricing strategies among vendors, with some retailers
consistently offering higher or lower prices across product categories.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Average price difference by vendor}
\NormalTok{price\_diff\_plot }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(vendor\_name) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{avg\_price\_difference =} \FunctionTok{mean}\NormalTok{(price\_difference, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(vendor\_name, avg\_price\_difference), }\AttributeTok{y =}\NormalTok{ avg\_price\_difference)) }\SpecialCharTok{+}
  \FunctionTok{geom\_bar}\NormalTok{(}\AttributeTok{stat =} \StringTok{"identity"}\NormalTok{, }\AttributeTok{fill =} \StringTok{"coral"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Average Price Difference by Vendor"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Vendor"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Average Price Difference (CAD)"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\NormalTok{price\_diff\_plot}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-1.pdf}

Figure 2: Average Price Difference by Vendor. This bar plot shows the
average price change per vendor, highlighting retailers with the most
significant pricing adjustments. Positive differences suggest recent
price increases, while negative differences indicate reductions,
reflecting possible discounting or competitive pricing strategies.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Scatter plot of previous price vs. current price}
\NormalTok{price\_relationship\_plot }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(analysis\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ price\_old, }\AttributeTok{y =}\NormalTok{ price\_current)) }\SpecialCharTok{+}
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{alpha =} \FloatTok{0.4}\NormalTok{, }\AttributeTok{color =} \StringTok{"blue"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_smooth}\NormalTok{(}\AttributeTok{method =} \StringTok{"lm"}\NormalTok{, }\AttributeTok{color =} \StringTok{"red"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Relationship Between Previous and Current Prices"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Previous Price (CAD)"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Current Price (CAD)"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\NormalTok{price\_relationship\_plot}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
`geom_smooth()` using formula = 'y ~ x'
\end{verbatim}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-1.pdf}

Figure 3: Relationship Between Previous and Current Prices. This scatter
plot with a linear regression line shows the correlation between
previous and current prices. A positive relationship would indicate that
higher previous prices predict higher current prices, implying potential
price stability or gradual price changes in the grocery market.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Calculate mean and standard deviation of price\_difference}
\NormalTok{mean\_diff }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(analysis\_data}\SpecialCharTok{$}\NormalTok{price\_difference, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
\NormalTok{sd\_diff }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(analysis\_data}\SpecialCharTok{$}\NormalTok{price\_difference, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}

\CommentTok{\# Filter out extreme values beyond 3 standard deviations}
\NormalTok{filtered\_data }\OtherTok{\textless{}{-}}\NormalTok{ analysis\_data }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(price\_difference }\SpecialCharTok{\textgreater{}=}\NormalTok{ (mean\_diff }\SpecialCharTok{{-}} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ sd\_diff),}
\NormalTok{         price\_difference }\SpecialCharTok{\textless{}=}\NormalTok{ (mean\_diff }\SpecialCharTok{+} \DecValTok{3} \SpecialCharTok{*}\NormalTok{ sd\_diff))}

\CommentTok{\# Plot histogram with filtered data}
\NormalTok{price\_difference\_hist }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(filtered\_data, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ price\_difference)) }\SpecialCharTok{+}
  \FunctionTok{geom\_histogram}\NormalTok{(}\AttributeTok{bins =} \DecValTok{30}\NormalTok{, }\AttributeTok{fill =} \StringTok{"lightgreen"}\NormalTok{, }\AttributeTok{color =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Distribution of Price Differences (Filtered)"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Price Difference (CAD)"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Frequency"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\NormalTok{price\_difference\_hist}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-1.pdf}

Figure 4: Distribution of Price Differences (Filtered). This histogram
illustrates the frequency of price changes across products, with extreme
values beyond three standard deviations removed for clarity. The
concentration around zero suggests that small price adjustments are most
common, while the presence of both negative and positive values
indicates instances of both price increases and decreases. This
distribution provides insight into the stability and variability of
pricing across vendors.

@@

\bibitem[\citeproctext]{ref-palmerpenguins}
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
\emph{{palmerpenguins: Palmer Archipelago (Antarctica) penguin data}}.
\url{https://doi.org/10.5281/zenodo.3960218}.

>>>>

@@

@@

\includegraphics{paper_files/figure-pdf/fig-avg-curr-price-1.pdf}

\caption{\label{fig-avg-curr-price}Average Current Price by Vendor. This
bar plot shows the average price of products sold by each grocery vendor
in Canadian dollars (CAD). Variations in pricing suggest differences in
market positioning or pricing strategies among vendors, with some
retailers consistently offering higher or lower prices across product
categories.}

@@

\includegraphics{paper_files/figure-pdf/fig-avg-price-diff-1.pdf}

\caption{\label{fig-avg-price-diff}Average Price Difference by Vendor.
This bar plot shows the average price change per vendor, highlighting
retailers with the most significant pricing adjustments. Positive
differences suggest recent price increases, while negative differences
indicate reductions, reflecting possible discounting or competitive
pricing strategies.}

@@

\includegraphics{paper_files/figure-pdf/fig-past-curr-1.pdf}

\caption{\label{fig-past-curr}Relationship Between Previous and Current
Prices. This scatter plot with a linear regression line shows the
correlation between previous and current prices. A positive relationship
would indicate that higher previous prices predict higher current
prices, implying potential price stability or gradual price changes in
the grocery market.}

@@

\includegraphics{paper_files/figure-pdf/fig-dist-price-1.pdf}

\caption{\label{fig-dist-price}Relationship Between Previous and Current
Prices. This scatter plot with a linear regression line shows the
correlation between previous and current prices. A positive relationship
would indicate that higher previous prices predict higher current
prices, implying potential price stability or gradual price changes in
the grocery market.}

@@
